### 2017-12-18 manuscript.rmd
fixed supplementary figs captions

#####Stochastic Character maps
```{r tentilla, echo=F, message=F,warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla"}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla_obj <- densityMap(tentilla_sim,plot=FALSE)
tentilla_obj$cols[1:length(tentilla_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla_obj$cols))
plot(tentilla_obj)
```

```{r tentilla2, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included"}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim2 %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla2_obj <- densityMap(tentilla_sim2, plot=FALSE)
tentilla2_obj$cols[1:length(tentilla2_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla2_obj$cols))
plot(tentilla2_obj)
```

```{r nectosome, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
nectosome_obj <- densityMap(nectosome_sim, plot=FALSE)
nectosome_obj$cols[1:length(nectosome_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(nectosome_obj$cols))
plot(nectosome_obj)
```

>>>>

#####Stochastic Character maps
```{r tentilla, echo=F, message=F,warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as not bearing tentilla."}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla_obj <- densityMap(tentilla_sim,plot=FALSE)
tentilla_obj$cols[1:length(tentilla_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla_obj$cols))
plot(tentilla_obj)
```

```{r tentilla2, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as bearing tentilla."}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim2 %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla2_obj <- densityMap(tentilla_sim2, plot=FALSE)
tentilla2_obj$cols[1:length(tentilla2_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla2_obj$cols))
plot(tentilla2_obj)
```

```{r nectosome, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome."}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
nectosome_obj <- densityMap(nectosome_sim, plot=FALSE)
nectosome_obj$cols[1:length(nectosome_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(nectosome_obj$cols))
plot(nectosome_obj)
```
